---
title: "Git1Rstudio2Test"
author: "Molly Simonis"
date: "June 2, 2019"
output: html_document
---

##Beginning instructions from https://happygitwithr.com/rstudio-git-github.html

#12.2 Make a repo on GitHub

Go to https://github.com and make sure you are logged in.

Click green “New repository” button. Or, if you are on your own profile page, click on “Repositories”, then click the green “New” button.

How to fill this in:

Repository name: myrepo (or whatever you wish, we’ll delete this soon anyway).

Description: “testing my setup” (or whatever, but some text is good for the README).

Public.

YES Initialize this repository with a README.

For everything else, just accept the default.

Click big green button “Create repository.”

Copy the HTTPS clone URL to your clipboard via the green “Clone or Download” button.

#12.3 Clone the new GitHub repository to your computer via RStudio

In RStudio, start a new Project:

File > New Project > Version Control > Git. In “Repository URL”, paste the URL of your new GitHub repository. It will be something like this https://github.com/jennybc/myrepo.git.

Do you NOT see an option to get the Project from Version Control? Restart RStudio and try again. Still no luck? Go to chapter 13 for tips on how to help RStudio find Git.

Accept the default project directory name, e.g. myrepo, which coincides with the GitHub repo name.

Take charge of – or at least notice! – where the Project will be saved locally. A common rookie mistake is to have no idea where you are saving files or what your working directory is. Pay attention. Be intentional. Personally, I would do this in ~/tmp.

I suggest you check “Open in new session”, as that’s what you’ll usually do in real life.

Click “Create Project”.

You should find yourself in a new local RStudio Project that represents the new test repo we just created on GitHub. This should download the README.md file from GitHub. 
Look in RStudio’s file browser pane for the README.md file.

#12.4 Make local changes, save, commit

From RStudio, modify the README.md file, e.g., by adding the line “This is a line from RStudio”. Save your changes.

Commit these changes to your local repo. How?

From RStudio:

Click the “Git” tab in upper right pane.

Check “Staged” box for README.md.

If you’re not already in the Git pop-up, click “Commit”.

Type a message in “Commit message”, such as “Commit from RStudio”.

Click “Commit”.

#12.5 Push your local changes online to GitHub

Click the green “Push” button to send your local changes to GitHub. If you are challenged for username and password, provide them (but see below). You should see some message along these lines.

#12.6 Confirm the local change propagated to the GitHub remote

Go back to the browser. I assume we’re still viewing your new GitHub repo.

Refresh.

You should see the new “This is a line from RStudio” in the README.

If you click on “commits”, you should see one with the message “Commit from RStudio”.

If you have made it this far, you are DONE with set up.

##Practice
Create an rmd file into your new git repostiory
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages('usethis')
#library(usethis)
library(tidyverse)
library(ggplot2)
```

Make a table and plot
```{r}
x<- seq(1, 10, 1)
y<- seq(1, 50, 5)

df<- as.data.frame(cbind(x, y))

plot(df$x, df$y)
```

Commit and push to git
```{r}
#save rmd
#check it in the git panel under 'staged'
#hit commit 
#make a comment and mark the date and time
#hit commit
#hit push
#Check your repo online
```

Try adding your data to the new project
```{r}
#place a .csv file in the project file in your windows explorer (or mac equivilent)
#read in table
sample<- read.csv('test_data.csv')

#try an analyses
sample_lm<- lm(Count ~ Year*Site, data = sample) 
sample_anova<- anova(sample_lm)
sample_lm_output<- summary(sample_lm)

#try a plot
ggplot(data = sample, aes(x = Site, y = Count, color = Year)) +
  geom_point(aes(x = Site, y = Count, color = Year), position = 'jitter') +
  geom_boxplot(aes(x = Site, y = Count), alpha = 0.5)
```

Commit and push csv and changes to the rmd
```{r}
#try on your own using steps from previous "commit and push" chunk
```

Try putting your plot as a jpeg file in the repository
```{r}
#save plot as a jpeg in the project directory
#commit and push
```

Now lets try one more time by committing and pushing analyses outputs
```{r}
#run your lm analyses objects and copy and past the output into this chunk
##don't forget to place '#' at the beginning of the output lines!
###TIP: hold down 'Alt' before clicking at the beginning of the firstoutput line, and scroll your cursor down the entire output. You will only need to click and hit '#' once! :)

sample_anova
#Analysis of Variance Table

#Response: Count
#          Df Sum Sq Mean Sq F value  Pr(>F)  
#Year       1   1.07   1.066  0.1402 0.70915  
#Site       1  21.00  21.002  2.7617 0.10089  
#Year:Site  1  33.36  33.361  4.3868 0.03974 *
#Residuals 72 547.56   7.605                  
#---
#Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1


sample_lm_output
#Call:
#lm(formula = Count ~ Year * Site, data = sample)

#Residuals:
#    Min      1Q  Median      3Q     Max 
#-4.7020 -2.2066 -0.1157  2.2011  5.6323 

#Coefficients:
#             Estimate Std. Error t value Pr(>|t|)   
#(Intercept)   3.39516    0.99831   3.401   0.0011 **
#Year          0.13893    0.05280   2.631   0.0104 * 
#Sitetrx       1.46566    2.08643   0.702   0.4847   
#Year:Sitetrx -0.13012    0.06213  -2.094   0.0397 * 
#---
#Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
#
#Residual standard error: 2.758 on 72 degrees of freedom
#Multiple R-squared:  0.09193,	Adjusted R-squared:  0.05409 
#F-statistic:  2.43 on 3 and 72 DF,  p-value: 0.0722

#Go through your commit and push steps
```


